Radar code documentation

### 2022-03-15 doc/msp_code.tex
use j=0 for sums over codes
update doc

\section{Introduction}
A binary phase radar code is presented which has optimal noise canceling properties, intrinsically measures the entire range at once (assuming that it is finite) and supports arbitrary radar duty cycles.
\section{Mathematical description}
We assume that the radar code $\epsilon$ has length $L$ and is periodic $\epsilon_i = \epsilon_{i + L}$.
Furthermore, the radar code is normalized and binary phase, meaning that $\epsilon_i \in [-1, 1]$.
This implies that $\epsilon_i^*\epsilon_i = 1$, where we could drop the complex conjugate symbol, but we will keep it to show that the formalism also applies to poly-phase codes.
We further assume that the radar code is transmitted indefinitely.\\
Figure \ref{fig:sketch} illustrates the measurement process of the unmodulated code.
In the figure, it can be seen that the measured voltage $m_i$ at time index $i$ can be calculated by summing over the scattered voltages $V^{(k)}_i$ which are modulated with the radar code,
\begin{equation}
\sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i = m_i
\end{equation}
where $N$ is the maximum altitude index considered and $k$ is the altitude index.
Note that $N$ must be finite.\\
Now, the estimator
\begin{equation}
\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^L_{j=1}\epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}.
\end{equation}
for the autocorrelation function $R$ at altitude $h$ and lag $\Delta$ is considered.
In the following, it will be shown that this estimator is unbiased, if the code fulfills a certain condition.\\
We calculate the expectation value of the estimator
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
=\frac{1}{L}\sum^L_{j=1} \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
\end{equation}
where the double sum was reduced to a single sum symbol, because scattered voltages of different altitudes do not correlate.
Now, we use the definition of the autocorrelation function $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$, where we assume a wide sense stationary process during the time it takes to transmit the code once.
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
= R^{(h)}_\Delta + \sum_{k=0,k\neq h}^{N-1}R^{(k)}_\Delta
\left[ \frac{1}{L}\sum^L_{j=1}\epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k}\right].
\end{equation}
The estimator is unbiased if the expression in the square brackets is zero.
Let $w = k - h$ and note that $w \neq 0$ and $|w| < N$.
Using the periodicity it can be shown that the condition is equivalent to
\begin{equation}
0 = \frac{1}{L}\sum^L_{j=1}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
\label{eq:cond}
\end{equation}
In the next section, solutions of this equation are discussed.

\section{Solving the code condition}
The condition given by \eqref{eq:cond} is trivially fulfilled for pseudo random numbers if $L \rightarrow \infty$.
However, the measurement would have no (definitive) time resolution in this case.
With a brute-force computer search it can be shown that solutions do exist, when a finite $\Delta \in [1, M]$ is assumed, where $M$ is the total number of measurement points in the auto correlation function.
If a code fulfills the condition it will be referred to as a valid code.
Note that an inversion or a (cyclic) shift of any valid code is also a valid code.
Thus, only codes which start with a $+$ (or $-$) must be checked.
Further, all codes which do not contain the sequence $+-$ must be a constant sequence.
Thus is sufficient to check codes which start with $+$ and end with $-$.
However there are still many codes which are cyclic versions of other codes.

@@

Let
\begin{equation}
\gamma_{j, i} = \epsilon_{j + i}^*\epsilon_{j}
\end{equation}
so that the autocorrelation function of the code can be written as
\begin{equation}
s_i = \sum_{j=1}^{L}\gamma_{j, i}.
\end{equation}
We want to satisfy conditions of the type $s_i=0$ for certain values of $i$, which requires solving the inverse problem, which is, calculating $\epsilon$ given a certain $\gamma$.
The recursive equation
\begin{equation}
\epsilon_{j + i}^* = \gamma_{j, i} \epsilon_{j}
\end{equation}
follows directly from the definition of $\gamma$.
It can be solved by plugging it into itself till $\epsilon_j$ is encountered again, which yields the following condition for the existence of a solution
\begin{equation}
\gamma_{k, i} = \prod_{j=1}^{L/d - 1}\gamma_{jd + k, i}
\end{equation}
where $d=d(i)$ is the greatest common denominator of $L$ and $i$ and $k \in [1, d]$.
Thus, we have $d$ conditions, which removes $d$ degrees of freedom from $\gamma_{j, i}$, meaning that for each value of $i$, a number of $L-d$ bits can be chosen arbitrarily without violating the condition above.\\
We have now formally solved the problem for a single, fixed value of $i$.
In order to satisfy a problem in which two values of $i$ are allowed, called $i_1$ and $i_2$, we calculate the sets of corresponding solutions $\gamma_{j, i}$ and $\gamma'_{j, i'}$ first.

\begin{equation}
s'_i s_i = \sum_{j'=1}^{L}\sum_{j=1}^{L}\gamma'_{j', i}\gamma_{j, i}.
\end{equation}

@@

@@

\section{Modulating the code}

@@

\section{Properties of the code}

\section{Simulation}
\subsection{Monte Carlo Generation}
The most straight-forward approach to generate random numbers following a wide-sense stationary process is as follows:
\begin{equation}
R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle
\end{equation}
where $R^{(h)}_{jk}$ is interpreted (for some fixed $h$) as a correlation matrix for the random vector $V_{j}^{(h)}$ which is to be generated.
We can satisfy the correlation properties by a linear transformation
\begin{equation}
V_j^{(h)} = \sum_{i} T_{ji}f_i
\end{equation}
where $T_{ji}$ must be of toeplitz type and $f_i$ are uncorrelated standard normal Gaussian circular-symmetric random variables with $\langle f_i f_j \rangle = \delta_{ij}$.
This yields
\begin{equation}
R^{(h)}_{jk} = \sum_{i,l} \langle (T_{ji}f_i)^* T_{kl}f_l \rangle = \sum_{i} T_{ji}^* T_{ki}.
\end{equation}
Using that the matrix $T$ is symmetric and seeing that $R^{(h)}_{jk}$ must be positive semidefinite (as it is a covariance matrix) we can calculate $T$ with some square root of matrix algorithm.\\
However all of this can be done more efficiently by using the time stationary of the process.
Note that $T$ is of toeplitz type simply means that we actually need a convolution of $f$ with $T$ where $T$ must be symmetric with a length of at least $2M + 1$ so that the points up to $M + 1$ can be correlated.
However, the generated time series would not have the true correlation properties of the ACF if it is truncated after $M+1$.
The ACF can be either truncated after $n-1$, where $n$ is the total length of the time series, or when the ACF approaches approximately zero.
Now, denote the length of the ACF by $K$.
The convolution is given by
\begin{equation}
V_j^{(h)} = \sum_{i=1-K}^{K-1} T_{i}f_{j - i}.
\end{equation}
It follows that,
\begin{equation}
R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle = \sum_{l=1-K}^{K-1} \sum_{m=1 - K}^{K-1} T_{l} T_{m} \langle f_{j - l} f_{k - m} \rangle.
\end{equation}
Using that $\langle f_{j - l} f_{k - m} \rangle = \delta_{m, k - j + l}$ and substituting $\Delta=j-k$ yields
\begin{equation}
R^{(h)}_\Delta = \sum_{i=1-K}^{K-1} T_{i} T_{i - \Delta}
\end{equation}
where it is assumed that $T$ is zero padded for all indices which fall out of range.
Applying a Fourier transform over $\Delta$ on both sides results in
\begin{equation}
\mathrm{DCT}[R^{(h)}]_j = \sum_{i=1-K}^{K-1} T_{i}\mathrm{DTFT}[T_{i - \Delta}]_j.
\end{equation}
From the definition of the $\mathrm{DTFT}$ follows that
\begin{equation}
\mathrm{DCT}[R^{(h)}]_j = \sum_{l=1-K}^{K-1} T_{l}\exp\left(\frac{i2\pi lj}{2K-1} \right) \mathrm{DCT}[T]_j,
\end{equation}
using the definition of the Fourier transform again results in
\begin{equation}
\mathrm{DCT}[R^{(h)}]_j = (2K - 1)\left( \mathrm{DCT}[T]_j \right)^2.
\end{equation}
Now there are two options: Either one solves for $T$ and does the convolution in the time domain, or one solves for the Fourier transform of $T$ and does the convolution in Fourier space.
Which one is faster depends on the choice of $K$.
The first approach is preferred when $K$ is fixed which results in an asymptotic runtime of $\mathcal{O}(Kn)$.
In the case $K=n$ latter approach is preferred as it results in a runtime of $\mathcal{O}(n\log(n))$.
However, choosing $K=n$ has not a real practical use case, as the ACF can always be cut off at small value, in the sense that $M \gtrsim K$.

>>>>

\section{Introduction}
A novel binary phase radar code is presented which has optimal noise canceling properties for the lag value estimator being considered.
Furthermore, it is shown that the estimator is close to the Cramér–Rao bound.
The code intrinsically measures the entire range at once, which must be finite.
\section{Estimator and code requirement for zero bias}
We assume that the radar code $\epsilon$ has length $L$ and is periodic $\epsilon_i = \epsilon_{i + L}$.
Furthermore, the radar code is normalized and binary phase, meaning that $\epsilon_i \in [-1, 1]$.
This implies that $\epsilon_i^*\epsilon_i = 1$, where we could drop the complex conjugate symbol, but we will keep it to show that the formalism also applies to poly-phase codes.
We further assume that the radar code is transmitted indefinitely.\\
Figure \ref{fig:sketch} illustrates the measurement process of the unmodulated code.
In the figure, it can be seen that the measured voltage $m_i$ at time index $i$ can be calculated by summing over the scattered voltages $V^{(k)}_i$ which are modulated with the radar code,
\begin{equation}
m_i = \sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i
\end{equation}
where $N$ is the maximum altitude index considered and $k$ is the altitude index.
Note that $N$ must be finite.\\
Now, the estimator
\begin{equation}
\hat{R}^{(h)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}m_{j + \Delta + h}^* \epsilon_j^*m_{j + h}.
\end{equation}
for the autocorrelation function $R$ at altitude $h$ and lag $\Delta > 0$ is introduced.
In the following, it will be shown that this estimator is unbiased, if the code fulfills a certain condition.\\
We calculate the expectation value of the estimator
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
=\frac{1}{L}\sum^{L - 1}_{j=0} \epsilon_{j + \Delta}\epsilon_j^* \sum_{k=0}^{N-1} \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k} \langle (V^{(k)}_{j + \Delta})^*V^{(k)}_j \rangle
\end{equation}
where the double sum was reduced to a single sum symbol, because scattered voltages of different altitudes do not correlate.
Now, we use the definition of the autocorrelation function $\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle = R^{(k)}_\Delta$, where we assume a wide sense stationary process during the time it takes to transmit the code once.
\begin{equation}
\langle \hat{R}^{(h)}_\Delta \rangle
= R^{(h)}_\Delta + \sum_{k=0,k\neq h}^{N-1}R^{(k)}_\Delta
\left[ \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j + \Delta}\epsilon_j^* \epsilon_{j+\Delta+h-k}^*\epsilon_{j+h-k}\right].
\end{equation}
The estimator is unbiased if the expression in the square brackets is zero.
Let $w = k - h$ and note that $w \neq 0$ and $|w| < N$.
Using the periodicity it can be shown that the condition is equivalent to
\begin{equation}
0 = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
\label{eq:cond}
\end{equation}
\subsection{Bias of a random code}
For a random code, the condition is not exactly zero
\begin{equation}
r = \frac{1}{L}\sum^{L-1}_{j=0}\epsilon_{j}\epsilon_{j+w}^* \epsilon_{j+\Delta}^*\epsilon_{j + \Delta + w}.
\end{equation}
The variance is
\begin{equation}
\mathrm{Var}[r] = \frac{1}{L},
\end{equation}
which means that the result will be biased on average by
\begin{equation}
b^{(h)}_\Delta = \sum_{k=0,k\neq h}^{N-1}\frac{R^{(k)}_\Delta}{\sqrt{L}}
\end{equation}

\section{Optimizing the noise cancellation properties}
The variance is calculated by
\begin{equation}
\langle |\hat{R}^{(h)}_\Delta|^2 \rangle = \frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
\epsilon_{j_1} \epsilon_{j_1 + \Delta}
\epsilon_{j_2} \epsilon_{j_2 + \Delta}
\langle
m_{j_1 + \Delta + h} m_{j_1 + h}^*
m_{j_2 + \Delta + h}^* m_{j_2 + h}
\rangle
\end{equation}
using Isserli's theorem on the four product of Gaussian random numbers
\begin{equation}
\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] = \frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}
\epsilon_{j_1} \epsilon_{j_1 + \Delta}
\epsilon_{j_2} \epsilon_{j_2 + \Delta}
\langle m_{j_1 + \Delta + h} m_{j_2 + \Delta + h}^* \rangle
\langle m_{j_2 + h} m_{j_1 + h}^* \rangle
\end{equation}
and using $\langle m_i m_j \rangle = 0$ yields the desired variance.
Calculating the remaining expectation values
\begin{equation}
\langle m_{j_1}^*m_{j_2} \rangle = \sum_{k=0}^{N-1} \epsilon_{j_1-k} \epsilon_{j_2-k} R_{|j_1-j_2|}^{(k)}
\end{equation}
and substituting it into the previous expression result in
\begin{equation}
\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] = \frac{1}{L^2}\sum^{L-1}_{j_1=0}\sum^{L-1}_{j_2=0}\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}
\hat{\epsilon}_{j_1}\hat{\epsilon}_{j_2} R_{|j_1-j_2|}^{(k_1)} R_{|j_1-j_2|}^{(k_2)}
\end{equation}
where
\begin{equation}
\hat{\epsilon}_j = \epsilon_j \epsilon_{j + \Delta} \epsilon_{j + h - k_2} \epsilon_{j + \Delta + h - k_1}
\end{equation}
was defined for brevity.
By making use of the symmetry in $j_1 \leftrightarrow j_2$ it can be shown that
\begin{equation}
\mathrm{Var}[ \hat{R}^{(h)}_\Delta ] = \frac{1}{L}\left(\sum_{k_1=0}^{N-1} R_{0}^{(k_1)} \right)^2 +
\frac{2}{L^2}\sum^{L-1}_{j_2=1}\sum^{L-1-j_2}_{j_1=0}\sum_{k_1=0}^{N-1}\sum_{k_2=0}^{N-1}
\hat{\epsilon}_{j_1}\hat{\epsilon}_{j_1+j_2} R_{|j_2|}^{(k_1)} R_{|j_2|}^{(k_2)}.
\end{equation}
Now, the unknown product of $R$ variables does no longer depend $j_1$, but the codes are summed over $j_1$.
For a random code of infinite length, the sum over $j_1$ will have zero expectation value.
However, for a finite code the sum over $j_1$ can be negative, yielding additional noise suppression.
The design of a code with maximal noise suppression appears to depend on the measurement results themselves.
All codes which fulfill the bias free condition yield basically the same amount of noise suppression and appear like a random code to the second term.
This gives effectively a standard deviation proportional to $N/L^{3/2}$ because $R$ drops exponentially with increasing $j_2$.
So a long code might be better than a short periodic one.

\section{Solving the code condition}
The condition given by \eqref{eq:cond} is trivially fulfilled for pseudo random numbers if $L \rightarrow \infty$.
However, the measurement would be biased and have no (definitive) time resolution in this case.
With a brute-force computer search it can be shown that solutions do exist, when a finite $\Delta \in [1, M]$ is assumed, where $M$ is the total number of measurement points in the auto correlation function.
If a code fulfills the condition it will be referred to as a valid code.
Note that an inversion or a (cyclic) shift of any valid code is also a valid code.
Thus, only codes which start with a $+$ (or $-$) must be checked.
Further, all codes which do not contain the sequence $+-$ must be a constant sequence.
Thus is sufficient to check codes which start with $+$ and end with $-$.
However there are still many codes which are cyclic versions of other codes.

@@

Let
\begin{equation}
\gamma_{j, i} = \epsilon_{j + i}^*\epsilon_{j}
\end{equation}
so that the autocorrelation function of the code can be written as
\begin{equation}
s_i = \sum_{j=0}^{L-1}\gamma_{j, i}.
\end{equation}
We want to satisfy conditions of the type $s_i=0$ for certain values of $i$, which requires solving the inverse problem, which is, calculating $\epsilon$ given a certain $\gamma$.
The recursive equation
\begin{equation}
\epsilon_{j + i}^* = \gamma_{j, i} \epsilon_{j}
\end{equation}
follows directly from the definition of $\gamma$.
It can be solved by plugging it into itself till $\epsilon_j$ is encountered again, which yields the following condition for the existence of a solution
\begin{equation}
\gamma_{k, i} = \prod_{j=1}^{L/d - 1}\gamma_{jd + k, i}
\end{equation}
where $d=d(i)$ is the greatest common denominator of $L$ and $i$ and $k \in [1, d]$.
Thus, we have $d$ conditions, which removes $d$ degrees of freedom from $\gamma_{j, i}$, meaning that for each value of $i$, a number of $L-d$ bits can be chosen arbitrarily without violating the condition above.\\
We have now formally solved the problem for a single, fixed value of $i$.
In order to satisfy a problem in which two values of $i$ are allowed, called $i_1$ and $i_2$, we calculate the sets of corresponding solutions $\gamma_{j, i}$ and $\gamma'_{j, i'}$ first.

\begin{equation}
s'_i s_i = \sum_{j'=0}^{L-1}\sum_{j=0}^{L-1}\gamma'_{j', i}\gamma_{j, i}.
\end{equation}

@@

longest run in the beginning
followed by an uneven number of runs
511111
5311

@@

\section{Modulating the code}
\subsection{Modulation with fixed code}

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{code_diagram_modulated.pdf}
	\caption{Range time diagram of the modulated version of the radar code with $S=3$.}
	\label{fig:modulated}
\end{figure}
\begin{equation}
m_{i,w} = \sum_{k=0}^{N-1} \epsilon_{i-k} \sum_{s=0}^{S-1} \gamma_{S-1-s} V^{(k, s + w)}_{i}
\end{equation}
\begin{equation}
d_{i,w} = \sum^{S-1}_{s=0} \gamma_{s} m_{i, s + w}
\end{equation}
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_2} \gamma_{S-1-s_1} V_i^{(k, s_1 + s_2 + w)}
\end{equation}
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k} \sum_{s_1=0}^{S-1} \sum^{S-1}_{s_2=0} \gamma_{s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + s_2 + w)}
\end{equation}
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\left[SV_i^{(k, S - 1 + w)}
+ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2} \gamma_{s_1 + s_2} V_i^{(k, S - 1 + s_1 + w)}
+ \sum_{s_1=1}^{S-1} \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2} V_i^{(k, S - 1 - s_1 + w)} \right]
\end{equation}
\begin{equation}
A_{s_1} = \sum^{S-1-s_1}_{s_2=0} \gamma_{s_2+s_1} \gamma_{s_2}\text{ for }s_1\in[0, S-1]
\end{equation}
\begin{equation}
d_{i,w} = \sum_{k=0}^{N-1}\epsilon_{i-k}\sum_{s=1-S}^{S-1} A_{|s|} V_i^{(k, S - 1 + s + w)}
\end{equation}
\begin{equation}
\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}d_{j + \Delta + h, w}^*
\epsilon_jd_{j + h, w}.
\end{equation}
\begin{equation}
\hat{R}^{(h, w)}_\Delta = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}
\sum_{k_1=0}^{N-1}\epsilon_{j+\Delta+h-k_1}\sum_{s_1=1-S}^{S-1} A_{|s_1|} \left(V_{j+\Delta+h}^{(k_1, S - 1 + s_1 + w)}\right)^*
\epsilon_j
\sum_{k_2=0}^{N-1}\epsilon_{j+h-k_2}\sum_{s_2=1-S}^{S-1} A_{|s_2|} V_{j+h}^{(k_2, S - 1 + s_2 + w)}
\end{equation}
\begin{equation}
\langle \hat{R}^{(h, w)}_\Delta \rangle = \frac{1}{L}\sum^{L-1}_{j=0}
\epsilon_{j + \Delta}
\sum_{k=0}^{N-1}\epsilon_{j+\Delta+h-k}\sum_{s_1=1-S}^{S-1} A_{|s_1|} 
\epsilon_j
\epsilon_{j+h-k}\sum_{s_2=1-S}^{S-1} A_{|s_2|} \left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle
\end{equation}
\begin{equation}
\left\langle \left(V_{j+\Delta+h}^{(k, S - 1 + s_1 + w)}\right)^* V_{j+h}^{(k, S - 1 + s_2 + w)} \right\rangle =
\delta_{s_1, s_2} R_\Delta^{(k, S-1+s_1+w)} +
\delta_{s_1, s_2+1} R_\Delta^{(k, S-1+s_1+w + 0.5)}/2 +
\delta_{s_1, s_2-1} R_\Delta^{(k, S-1+s_1+w - 0.5)}/2
\end{equation}
\begin{equation}
\langle \hat{R}^{(h, w)}_\Delta \rangle =
\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}+
\frac{1}{2}\sum_{s_1=1-S}^{S-2} A_{|s_1|}A_{|s_1+1|}R_\Delta^{(h, S-1+s_1+w+0.5)}+
\frac{1}{2}\sum_{s_1=2-S}^{S-1} A_{|s_1|}A_{|s_1-1|}R_\Delta^{(h, S-1+s_1+w-0.5)}
\end{equation}
if $\gamma$ is a barker code we have $A_{|i|}A_{|i+1|}=0$
\begin{equation}
\langle \hat{R}^{(h, w)}_\Delta \rangle =
\sum_{s_1=1-S}^{S-1} A^2_{|s_1|}R_\Delta^{(h, S-1+s_1+w)}
\end{equation}
so we find a biased estimator, where the signal is stronger by a factor
\begin{equation}
\frac{S^2}{S - 1}
\end{equation}
compared to the bias.
one can also deconvolute, to find an exact result.
\subsection{Modulation with variable code}
\subsection{Hypothesis on code length}

@@

\section{Simulation}
\subsection{Monte Carlo Generation}
The most straight-forward approach to generate random numbers following a wide-sense stationary process is as follows:
\begin{equation}
R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle
\end{equation}
where $R^{(h)}_{jk}$ is interpreted (for some fixed $h$) as a correlation matrix for the random vector $V_{j}^{(h)}$ which is to be generated.
We can satisfy the correlation properties by a linear transformation
\begin{equation}
V_j^{(h)} = \sum_{i} T_{ji}f_i
\end{equation}
where $T_{ji}$ must be of toeplitz type and $f_i$ are uncorrelated standard normal Gaussian circular-symmetric random variables with $\langle f_i f_j \rangle = \delta_{ij}$.
This yields
\begin{equation}
R^{(h)}_{jk} = \sum_{i,l} \langle (T_{ji}f_i)^* T_{kl}f_l \rangle = \sum_{i} T_{ji}^* T_{ki}.
\end{equation}
Using that the matrix $T$ is symmetric and seeing that $R^{(h)}_{jk}$ must be positive semidefinite (as it is a covariance matrix) we can calculate $T$ with some square root of matrix algorithm.\\
However all of this can be done more efficiently by using the time stationary of the process.
Note that $T$ is of toeplitz type simply means that we actually need a convolution of $f$ with $T$ where $T$ must be symmetric with a length of at least $2M + 1$ so that the points up to $M + 1$ can be correlated.
However, the generated time series would not have the true correlation properties of the ACF if it is truncated after $M+1$.
The ACF can be either truncated after $n-1$, where $n$ is the total length of the time series, or when the ACF approaches approximately zero.
Now, denote the length of the ACF by $K$.
The convolution is given by
\begin{equation}
V_j^{(h)} = \sum_{i=1-K}^{K-1} T_{i}f_{j - i}.
\end{equation}
It follows that,
\begin{equation}
R^{(h)}_{jk} = \langle (V_{j}^{(h)})^* V_k^{(h)} \rangle = \sum_{l=1-K}^{K-1} \sum_{m=1 - K}^{K-1} T_{l} T_{m} \langle f_{j - l} f_{k - m} \rangle.
\end{equation}
Using that $\langle f_{j - l} f_{k - m} \rangle = \delta_{m, k - j + l}$ and substituting $\Delta=j-k$ yields
\begin{equation}
R^{(h)}_\Delta = \sum_{i=1-K}^{K-1} T_{i} T_{i - \Delta}
\end{equation}
where it is assumed that $T$ is zero padded for all indices which fall out of range.
Applying a Fourier transform over $\Delta$ on both sides results in
\begin{equation}
\mathrm{DCT}[R^{(h)}]_j = \sum_{i=1-K}^{K-1} T_{i}\mathrm{DTFT}[T_{i - \Delta}]_j.
\end{equation}
From the definition of the $\mathrm{DTFT}$ follows that
\begin{equation}
\mathrm{DCT}[R^{(h)}]_j = \sum_{l=1-K}^{K-1} T_{l}\exp\left(\frac{i2\pi lj}{2K-1} \right) \mathrm{DCT}[T]_j,
\end{equation}
using the definition of the Fourier transform again results in
\begin{equation}
\mathrm{DCT}[R^{(h)}]_j = (2K - 1)\left( \mathrm{DCT}[T]_j \right)^2.
\end{equation}
Now there are two options: Either one solves for $T$ and does the convolution in the time domain, or one solves for the Fourier transform of $T$ and does the convolution in Fourier space.
Which one is faster depends on the choice of $K$.
The first approach is preferred when $K$ is fixed which results in an asymptotic runtime of $\mathcal{O}(Kn)$.
In the case $K=n$ latter approach is preferred as it results in a runtime of $\mathcal{O}(n\log(n))$.
However, choosing $K=n$ has not a real practical use case, as the ACF can always be cut off at small value, in the sense that $M \gtrsim K$.

\subsection{Discrete Fourier and Cosine Transform}
We define the Discrete Time Fourier Transform as
\begin{equation}
\mathrm{DTFT}[x]_n = \sum^{N-1}_{k=0} x_k \exp\left(-\frac{i2\pi kn}{N}\right)
\end{equation}
and its inverse by
\begin{equation}
\mathrm{DTFT}^{-1}[x]_n = \frac{1}{N}\sum^{N-1}_{k=0} x_k \exp\left(\frac{i2\pi kn}{N}\right).
\end{equation}
Sometimes, it can be handy to allow negative indices for a more ``natural'' representation.
In the case that $n$ is even
\begin{equation}
\mathrm{DTFT}^{-1}[\hat{x}]_n = \frac{1}{N}\sum^{N/2+1}_{k=-N/2+2} \hat{x}_k \exp\left(\frac{i2\pi kn}{N}\right)
\end{equation}
and in the uneven case
\begin{equation}
\mathrm{DTFT}^{-1}[\hat{x}]_n = \frac{1}{N}\sum^{(N-1)/2}_{k=-(N-1)/2} \hat{x}_k \exp\left(\frac{i2\pi kn}{N}\right).
\end{equation}
The Discrete Cosine Transform of Type I is defined as
\begin{equation}
\mathrm{DCT}[x']_n = x'_0 + x'_{N'-1}(-1)^n + 2\sum_{k=0}^{N'-1} x'_k \cos \left(\frac{\pi k n}{N'-1}  \right).
\end{equation}
and its inverse is given by
\begin{equation}
\mathrm{DCT}^{-1}[x']_n = \frac{\mathrm{DCT}[x']_n}{2(N'-1)}
\end{equation}
The $\mathrm{DCT}$ is equivalent to a $\mathrm{DTFT}$ for a symmetric input but it is faster and uses less memory.
More precisely, it can be shown that for $N=2(N'-1)$ and $x_i=x'_i$ for $i\in[0, N'-1]$ and $x_i=x'_{N-i}$ for $i\in[N', N-1]$ that
\begin{equation}
\mathrm{DTFT}^{-1}[x]_n = \mathrm{DCT}^{-1}[x']_n 
\end{equation}
where $n\in[0, N'-1]$.
\subsection{From the continuous Fourier transform to the DCT}
\begin{align}
R(\tau) &= \int_{-\infty}^{\infty} \exp(-2\pi i\omega\tau) S(\omega) \d \omega \\
&=2\int_{0}^{\infty} \cos(2\pi i\omega\tau) S(\omega) \d \omega
\end{align}
\begin{align}
S(j\Delta_\omega) &= S_j\\
R(j\Delta_\tau) &= R_j
\end{align}
As we only store a fixed number of samples, the period must be finite.
This means, that a periodic continuation beyond the last sample ($S_{N-1}$) must be specified.
In our case, even symmetry around $N-1$ is considered.
As the first and last sample's bins shall be centered around $\omega=0$ and $\omega=(N-1)\Delta_\omega$ respectively, they have half width, so the integral becomes
\begin{align}
R_k = S_0\Delta_\omega + \cos({2\pi (N-1) k\Delta_\omega \Delta_\tau}) S_{N-1} + 2\sum_{j=1}^{j=N-2}\cos({2\pi j k \Delta_\omega \Delta_\tau}) S_j \Delta_\omega 
\end{align}
The maximum frequency (half bandwidth in our case) is $B = \Delta_\omega (N - 1)$.
Now we can use the sampling theorem to find $\Delta_\tau = 1/(2B)$.
\begin{align}
R_k = \left(S_0 + (-1)^kS_{N-1} + 2\sum_{j=1}^{j=N-2}\cos \left(\frac{\pi j k}{N-1}  \right) S_j \right) \Delta_\omega
\end{align}
This is a type I DCT (Discrete Cosine Transform) according to scipy definition.

\section{A lower bound for the variance}

Assumptions made: monostatic radar, binary coded transmission, gaussian process
A lower bound for the variance of any ACF estimation independent of the estimator is to be calculate, by means of the Cramér–Rao bound.
What the radar measures (independent of the estimator) is
\begin{equation}
m_i=\sum_{k=0}^{N-1} \epsilon_{i-k} V^{(k)}_i.
\end{equation}
The parameters to be estimated are 
\begin{equation}
R^{(k)}_\Delta=\langle (V_{j+\Delta}^{(k)})^* V_j^{(k)} \rangle.
\end{equation}
The individual $m_i$ are random Gaussian distributed.
The information is contained in the correlations.
Define the probability density function $P = P(m_{1..n}, R^{(0..N-1)}_{1..M})$.
We need to calculate $P$.
the random variables $V^{(k)}_i$ are normally distributed with a correlation matrix of toeplitz type given by
\begin{equation}
\Sigma^{(k)}_{ij} = R_{i-j}^{(k)}
\end{equation}
then $m_i$ are Gaussian distributed according to
\begin{equation}
\Sigma_{ij} = \sum_{k=0}^{N-1} \epsilon_{i-k} \epsilon_{j-k} R_{|i-j|}^{(k)}.
\end{equation}
we note that the matrix is periodic with $\Sigma_{i,j} = \Sigma_{i+L,j+L}$
where we imagine the matrix to be infinite in size as the auto correlation never drops to precisely to zero.
The fisher information matrix for any zero mean Gaussian is
\begin{equation}
\mathcal{I}_{ij} = \frac{1}{2}\mathrm{tr}\left(\Sigma^{-1} \frac{\partial \Sigma}{\partial \theta_i} \Sigma^{-1} \frac{\partial \Sigma}{\partial \theta_j} \right)
\end{equation}
where each $\theta_i$ identifies exactly one parameter $\theta_i = R^{(k_i)}_{\Delta_i}$
\begin{equation}
\frac{\partial \Sigma_{ij}}{\partial \theta_p} = \epsilon_{i - k_p}\epsilon_{j - k_p}\delta_{|i-j|,\Delta_p}
\end{equation}
the fisher information matrix is
\begin{equation}
\mathcal{I}_{ij} = \frac{1}{2}\sum_{k_1, k_2, k_3, k_4}
\Sigma^{-1}_{k_1, k_2}
\epsilon_{k_2 - k_i}\epsilon_{k_3 - k_i}\delta_{|k_2-k_3|,\Delta_i}
\Sigma^{-1}_{k_3, k_4}
\epsilon_{k_4 - k_j}\epsilon_{k_1 - k_j}\delta_{|k_4-k_1|,\Delta_j}
\end{equation}
defining
\begin{equation}
\sigma_{\Delta_1, \Delta_2} =
\epsilon_{k_2 - k_i}\epsilon_{k_2 + \Delta_1 - k_i}
\epsilon_{k_1 - k_j}\epsilon_{k_1 + \Delta_2 - k_j}
\Sigma^{-1}_{k_1, k_2}
\Sigma^{-1}_{k_2 + \Delta_1, k_1 + \Delta_2}
\end{equation}
swapping $k_1 \leftrightarrow k_2$ and using symmetry of $\Sigma^{-1}$ it can be shown that
\begin{equation}
\sigma_{\Delta_1, \Delta_2} =
\epsilon_{k_1 - k_i}\epsilon_{k_1 + \Delta_1 - k_i}
\epsilon_{k_2 - k_j}\epsilon_{k_2 + \Delta_2 - k_j}
\Sigma^{-1}_{k_1, k_2}
\Sigma^{-1}_{k_1 + \Delta_1, k_2 + \Delta_2}
\end{equation}
using this definition results in
